\documentclass{report}%[11pt,a4paper]


\usepackage[a4paper, total={6in, 8in}]{geometry}
%\usepackage{float}
\usepackage{enumerate}
\usepackage{graphicx}
\graphicspath{ {images/} }
%\usepackage{url}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{makeidx}
%\makeindex

\setlength{\parindent}{0pt}

\begin{document}

\title{Work Diary}
\author{Scott Whitemore \& Brendon Veronese}

\floatstyle{boxed} 
\restylefloat{figure}

\maketitle

\section{Git Commits}
The following is a diary of work done for the purpose of studying the GCP.
The work can be found online\footnote{Here: https://github.com/BSvER1/GraphTheory-Exercises}. Note that not all commits (80 in total) are shown here. Only major events or changes to the code base are shown in this diary. Small changes to the code and tweaks to the algorithm were undertaken daily, with these changes committed when possible. 

\paragraph*{}August 27 - Prepatory data types and full permutation solver implemented. - Brendon

\paragraph*{}August 27 - Randomized order solver (RBB) implemented. - Scott.

\paragraph*{}August 28 - Ant Colony algorithm implemented. - Brendon

\paragraph*{}September 18 - Gravitational Swarm first pass implementation. - Brendon

\paragraph*{}September 19 - Flower Pollination Algorithm implemented. - Scott

\paragraph*{}September 26 - Create unmanaged routines to process graphs out of a folder automatically. Move towards cloud processing. - Brendon

\paragraph*{}October 8 - Genetic Algorithm implemented. - Scott

\paragraph*{}October 8 - Updates to code, set limits on runtime. Upload to cloud. - Brendon

\paragraph*{}October 12 - Reformat literature review. - Brendon

\paragraph*{}Many changes to literature review and codebase until 31st October. Final submission of literature review.



\end{document}